Radioastronomical image reconstruction using Kalman filter under ionospheric perturbations

### 2022-07-25 article/article.tex
update

@@

	We consider a set $\{x_k\}$ of $n$ vector as theoretical images taken at a regular time interval. Those images are measured by an antenna mesh which UV plane will be written $H$. Measurements vectors will be designated by $n$ measures $\{y_k\}$.\\
	We will consider the following model to describe time related evolutions and measure equation :
	$$
		\begin{cases}
			x_k = Ax_{k-1} + w_{k-1}\\
			y_k = Hx_k + v_k
		\end{cases}
	$$

	Where :
	\begin{itemize}
		\item $A$ is the linear evolutionary model between time $k-1$ and $k$, supposing evolution is time invariant
		\item $\{w_k\}$ are the additive evolutionary errors
		\item $\{v_k\}$ are the measurements noises
	\end{itemize}

@@

	This filter requires assumptions about

>>>>

	\subsection{General notations}

@@

	We consider a set $\{x_k\}$ of $n$ vector as theoretical images taken at a regular time interval. Those images are measured by an antenna mesh which UV plane will be written $H$, more generally written as observation model. Measurements vectors will be designated by $n$ measures $\{y_k\}$.\\
	We will consider the following model to describe time evolution and observation equation :
	$$
		\begin{cases}
			x_k = Ax_{k-1} + w_{k}\\
			y_k = Hx_k + v_k
		\end{cases}
	$$

	Where :
	\begin{itemize}
		\item $A$ is the linear state-transition model between time $k-1$ and $k$, supposing evolution is time invariant
		\item $\{w_k\}$ is the state noise sequence
		\item $\{v_k\}$ is the measurements noise sequence
	\end{itemize}

@@

	This filter requires more inputs to estimate the state of the system :
	\begin{itemize}
		\item $\{Q_k\}$, the covariance of the process noise sequence
		\item $\{R_k\}$, the covariance of the observation noise sequence
	\end{itemize}

	Which can be rewritten as
	$$
		\begin{cases}
			Q_k = \expval{w_{k-1}w_{k-1}^H} - \expval{w_{k-1}}\expval{w_{k-1}}^H \\
			R_k = \expval{v_{k}v_{k}^H} - \expval{v_k}\expval{v_k}^H \\
		\end{cases}
	$$
